Uncertainty Quantification in Multiscale Model

### 2024-11-06 paper.tex
update

In overcoming the challenges and achieving the multiscale model, uncertainties are introduced. 
While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces (need citation) and model the atomic coordinates using Newton’s equations, the atomic coordinates are not exactly the same as that modeled by the many-electron schr\"{o}dinger equation.
So the atomic coordinates, that is the molecule structures contain uncertainty which ultimately affects the charge dynamics. 
This is one source of uncertainty that have not been investigated.
But in our investigation, a fixed molecule structure is used and we do not consider this source of uncertainty. 
Secondly, state localization is not exactly a time dependent DFT process. 
But for amorphous OSCs used in this work, model noise from state localization is negligible and we do not consider the uncertainty brought by state localization.
Lastly, the exact functional for the exchange-correlation energy is unknown so approximations like the Local Density Approximation (LDA) or the Generalized Gradient Approximation (GGA) are used, resulting in exchange-correlation functional in practice. 
The accuracy of DFT depends heavily on the choice of the exchange-correlation functional whose accuracy is usually unknown for new synthesized molecules. 
As an advancement to improve accuracy, Hybrid-DFT incorporates a portion of exact HF exchange functional (HFX) from Hartree-Fock (HF) theory into the exchange-correlation functional, particularly for systems where DFT falls short. For example, the PBE0 functional has a portion of 0.25 HF exchange functional.

The charge dynamics is determined by CTRW transition rates, which depend on the electronic structures.
Since DFT is used to calculate the molecular electronic structures, the unknown exchange-correlation functional will bring uncertainties to the multiscale model. 
In particular, different hybrid-DFT functionals contain varying levels of Hartree Fock (HF) to represent the exchange-correlation potential. 
The effect of the uncertainty from the electronic structure level on the multiscale model is not yet explored in literatures. 
The goal of this work is to quantify the uncertainty effect of the exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model, with a particular focus on the uncertainty represented by different portional of HF exchange functional.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Molecule Dynamics Simulation}
The MD in the multiscale model is to use Newton's second law to update the atomic coordinate. Written in Hamilton equation, the equation of motion reads:
\begin{equation}
    \begin{cases}
        \frac{d \vec{r}_i}{dt} = \frac{\partial H^\text{MD} }{\partial \vec{p}_i} \\
        \frac{d \vec{p}_i}{dt} = -\frac{\partial H^\text{MD} }{\partial \vec{r}_i}
    \end{cases}
    \label{eq:Hamilton}
\end{equation}
for $i=1,\cdots,N_a$. Where $N_a$, $m_i$, $\vec{r}_i$, $\vec{p}_i$ are the atom number, atomic mass,  position vector and momentum, respectively. 
And the Hamiltonian $H$ reads:
$H^\text{MD}=\sum\limits_{i} \frac{|\vec{p}_i|^2}{2 m_i} + U(\vec{r}_1,\cdots,\vec{r}_{N_a})$.

In principle the potential energy function $U(\vec{r}_1,\cdots,\vec{r}_{N_a})$ of the system can be obtained from electronic structure models. As mentioned in the introduction, it is a very computationally expensive procedure, and without too much loss in precision, MD use empirical potentials that are designed for specific purposes.
The MD simulation performed using the GROMACS software package~\cite{berendsen_gromacs_1995}, employing a gromos54a7 type force field obtained via the tool Automated Topology Builder~\cite{stroet_automated_2018}. 
The procedure of the MD simulation in this work is as followed:...

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Time-of-flight Calculation}
The multiscale model defines a graph $\mathbf{G}$ with an adjacency matrix $\mathbf{W}$, where the nodes represent molecules and the edge weights $\omega_{ij}$ represent the Marcus rate from molecule $i$ to molecule $j$. 
The charge dynamics are modeled as a continuous-time random walk on this graph. In the time-of-flight (ToF) model, some vertices serve as \textit{Source} nodes, representing the electrode where charge carriers are injected, and some as \textit{Sink} nodes, where charge carriers are detected and the ToF is recorded.

@@

\begin{equation}
    v_\text{SS} = \sum_i \pi_i \sum_j \omega_{ij} || \vec{r}_{ij}||_2 = \mathbb{E}f(M_{\infty})
\end{equation} 
where $\omega_{ij}$ is the charge transition rate from molecule $i$ to molecule $j$, and $\vec{r}_{ij}=\vec{r}_j - \vec{r}_i$ is the center-of-mass (COM) distance vector. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this study, we investigate the hole-transporting organic semiconductor MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene).

Atomic charges and molecule polarizability $P_\text{iso}$ are crucial for evaluating molecular energy contributions from electrostatic and polarization effects. A physical property related to the overall atomic charges dipole moment at charge neutral state. 
To demonstration the effect of HFX on the atomic charges and molecule polarizability $P_\text{iso}$,
Figure \ref{fig:autogen_MADN} illustrates the dependence of the dipole moment $\mu$, isotropic polarizability $P_\text{iso}$, reorganization energy $\lambda$, and energy disorder $\sigma(E)$ on the Hartree-Fock exchange (HFX) parameter.

%
\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\textwidth]{figs/MADN_HFX/fig_autogen.pdf}
    \caption{(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters (denoted by $\alpha$).}
    \label{fig:autogen_MADN}
\end{figure}
%

Figure \ref{fig:autogen_MADN}(a) shows a decrease in the dipole moment with increasing HFX, exhibiting a notable drop at HFX = 0.25.

Figure \ref{fig:autogen_MADN}(b) demonstrates a linear decrease in isotropic polarizability for both neutral and charged MADN states as HFX increases from 0 to 0.25, indicating reduced molecular polarizability.

Figure \ref{fig:autogen_MADN}(c) indicates an increase in reorganization energy $\lambda$ with higher HFX, reflecting greater energy requirements for electronic adjustments during charge transfer. This increase is nonlinear compared to the linear decrease in $P_\text{iso}$.

Figure \ref{fig:autogen_MADN}(d) shows that the energy disorder $\sigma(E)$ for MADN are similar and close to \unit[0.08]{eV} under different HFX values.

The ToF and corresponding diffusive velocity $v_\text{ToF}$ are presented in Table \ref{tab:ToF_MADN_HFX}. For boundary conditions, the \textit{Source} region contains molecules with X-coordinates $0 < r^x_i < 0.5$ nm, and the \textit{Sink} region contains molecules with X-coordinates $8.5 < r^x_i < 9$ nm. We also consider scenarios without energy disorder to model systems where all molecules have uniform energy.

@@

Table \ref{tab:ToF_MADN_HFX} shows that as HFX increases from 0 to 0.25, the ToF with energy disorder increases by a factor of approximately 15, while without energy disorder, the increase factor is about 4. This increase in ToF is attributed to the rise in $\lambda$, changes in molecular energies, and variations in coupling elements.

Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using HFX = 0.25 (PBE0 functional) as a reference. The energies consistently fall within the range of -0.5 to -1.1 eV, with data points clustering near the diagonal line, indicating similar molecular energies regardless of HFX variation.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterE_qmmm.pdf}
    \caption{Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
    \label{fig:E_qmmm_MADN}
\end{figure}

Figures \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} show that both electrostatic and polarization energies remain consistent across HFX values from 0 to 0.25, further clustering near the diagonal.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterEstat_qmmm.pdf}
    \caption{Scatter plot of MADN electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
    \label{fig:Estat_qmmm_MADN}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterEdip_qmmm.pdf}
    \caption{Scatter plot of MADN polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
    \label{fig:Edip_qmmm_MADN}
\end{figure}

@@

The coupling element obtained with different HFX for each molecular pair compared to that obtained with HFX=0.25 is shown in the scatter plot Fig. \ref{fig:J_MADN}.
\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterJ_all.pdf}
    \caption{Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
    \label{fig:J_MADN}
\end{figure}

The distribution of $\log_{10} J^2$ has a range of -14 to -2, and for all HFX values, the distribution has a peak at around -5. 
For large values $\log_{10} J^2 < -5$ the coupling element remains consistent across HFX values from 0 to 0.25, while for large values $\log_{10} J^2 > -5$, the calculated coupling elements for a specific molecular pair can have large variation due to HFX values.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{figs/MADN_HFX/fig_network_all.pdf}
    \caption{The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$. The molecular systems obtained by different HFX are colored according to the legend.}
    \label{fig:J_percolate}
\end{figure}
After performing percolation algorithm, Figure \ref{fig:J_percolate} shows the dependence of $\max({N_\text{sub}})$ on the critical value $J_c$. When $\log_{10} J_c^2 < -4.5$, $\max({N_\text{sub}})$ is 1000, meaning that removing all the edges with $J^2 < 3.1 \times 10^{-5}$ the 1000 vertexes still form a connected graph. 
But when removing the edges with $J^2 < 3.1 \times 10^{-4}$ ( corresponding to $J_c > -3.5$), the maximum size subgraph is 600, and it quickly decreases as $J_c$ increases, showing a phase transition. 
So the dominated coupling elements are those with $\log_{10} J_c^2 > -4.5$. 
And the variation in small $J$ due to HFX has less impact on the charge dynamics.

@@

\subsection{ToF Distribution}
The ToF is calculated from electronic structure ($E$, $\lambda$ and $\log_{10}(J^2)$) data, that is, ToF is a function with the input of all electronic structure parameters:
\begin{equation}
    %\tau = g(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \}) \;
    \tau = g(x_1, x_2, \cdots, x_{N_d})
\end{equation}
The input $(x_1, x_2, \cdots, x_{N_d})$ represents the collection of the parameters $$(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \})$$  where $N_d$ is the parameter dimension, that is the number of input parameters. 
And $\{E_i|i=1,2,\cdots,N \}$ is the ordered set whose elements are the molecule energy,
$\{J_{ij}|i,j=1,2,\cdots,N \}$ is the ordered set whose elements are the coupling elements.

Since the exchange-correlation functional is not known and each molecule has a slightly different structure compared to the optimized structure, each parameter has uncertain. 
To estimate the uncertainty, we consider the maximum amount of uncertainties according to the obtained $(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \})$ with the six different HFX.
To achieve this, each parameter can be modeled as a normal distribution with the mean and standard deviation obtained by the maximum likelihood estimation. For a normal distribution, they are the HFX sample mean and standard deviation, respectively.

Then Monte Carlo scheme is used to estimate the distribution of the ToF. The Monte Carlo scheme has the procedure:
\begin{enumerate}
\item For all $i,j=1,2,\cdots, Nd$, obtain a realization $(x_1, x_2, \cdots, x_{N_d})$ where each parameter has the normal distribution, meaning: $\lambda_i \in \mathcal{N}(\bar{\lambda}_i, \sigma_{\lambda_i})$, $E_i \in \mathcal{N}(\bar{E}_i, \sigma_{E_i})$, $J_{ij} \in \mathcal{N}(\bar{J}_{ij}, \sigma_{J_{ij}})$. 
\item Calculate ToF using the sampled data set $(x_1, x_2, \cdots, x_{Nd})$. 
\item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain ToFs. Plot the distribution of the ToFs.
\item Fit the distribution of $log_{10}(\text{ToF})$ to Gamma distribution.
\end{enumerate}

The distribution of ToF calculated as the CTMC where transition parameters are varied is unknown, so we attempt to fit the distribution of ToF to Gamma distribution. The reason is as followed.

From equation \ref{eq:hitting_time}, the ToF can be considered as the some combination of occupation time in the molecules, which is $log_{10}(\omega_{i}^{-1})$. 
When the parameters $E, J_{ij}, \lambda_{ij}$ are normally distributed random variables, the calculated ToF shows that variables $E,\lambda_{ij}$ has a larger influence than $J_{ij}$. 
The Marcus rate uses $E,\lambda_{ij}$ in the exponential form. If $\Delta E$ is normally distributed, then $log_{10}(\omega_{i}^{-1})$ is Gamma distributed. 
Since $E$ has greater influence to ToF than $\lambda_{ij}, J_{ij}$ and to be consistent, Gamma distribution is used to fit the Monte Carlo sampled ToF in all the investigated cases.

>>>>

In overcoming the challenges and achieving the multiscale model, uncertainties are introduced. 
While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces (need citation) and model the atomic coordinates using Newton’s equations, the atomic coordinates are not exactly the same as that modeled by the many-electron schr\"{o}dinger equation.
So the atomic coordinates, that is the molecule structures contain uncertainty which ultimately affects the charge dynamics. 
This is one source of uncertainty that have not been investigated.
But in our investigation, a fixed molecule structure is used and we do not consider this source of uncertainty. 
Secondly, state localization is not exactly a time dependent DFT process. 
But for amorphous OSCs used in this work, model noise from state localization is negligible and we do not consider the uncertainty brought by state localization.
Lastly, the exact functional for the exchange-correlation energy is unknown so approximations like the Local Density Approximation (LDA) or the Generalized Gradient Approximation (GGA) are used, resulting in exchange-correlation functional in practice. 
The accuracy of DFT depends heavily on the choice of the exchange-correlation functional whose accuracy is usually unknown for new synthesized molecules. 
As an advancement to improve accuracy, Hybrid-DFT incorporates a portion $\alpha$ of exact HF exchange functional (HFX) from Hartree-Fock (HF) theory into the exchange-correlation functional, particularly for systems where DFT falls short. For example, the PBE0 functional has a portion of 0.25 HF exchange functional.

The charge dynamics is determined by CTRW transition rates, which depend on the electronic structures.
Since DFT is used to calculate the molecular electronic structures, the unknown exchange-correlation functional will bring uncertainties to the multiscale model. 
In particular, different hybrid-DFT functionals contain varying levels of HFX to represent the exchange-correlation potential. 
The effect of the uncertainty from the electronic structure level on the multiscale model is not yet explored in literatures. 
The goal of this work is to quantify the uncertainty effect of the exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model, with a particular focus on the uncertainty represented by different portional of HFX.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Molecule Dynamics Simulation}
\begin{comment}
    The MD in the multiscale model is to use Newton's second law to update the atomic coordinate. Written in Hamilton equation, the equation of motion reads:
\begin{equation}
    \begin{cases}
        \frac{d \vec{r}_i}{dt} = \frac{\partial H^\text{MD} }{\partial \vec{p}_i} \\
        \frac{d \vec{p}_i}{dt} = -\frac{\partial H^\text{MD} }{\partial \vec{r}_i}
    \end{cases}
    \label{eq:Hamilton}
\end{equation}
for $i=1,\cdots,N_a$. Where $N_a$, $m_i$, $\vec{r}_i$, $\vec{p}_i$ are the atom number, atomic mass,  position vector and momentum, respectively. 
And the Hamiltonian $H$ reads:
$H^\text{MD}=\sum\limits_{i} \frac{|\vec{p}_i|^2}{2 m_i} + U(\vec{r}_1,\cdots,\vec{r}_{N_a})$.

In principle the potential energy function $U(\vec{r}_1,\cdots,\vec{r}_{N_a})$ of the system can be obtained from electronic structure models. As mentioned in the introduction, it is a very computationally expensive procedure, and without too much loss in precision, MD use empirical potentials that are designed for specific purposes.
The MD simulation performed using the GROMACS software package~\cite{berendsen_gromacs_1995}, employing a gromos54a7 type force field obtained via the tool Automated Topology Builder~\cite{stroet_automated_2018}. 
The procedure of the MD simulation in this work is as followed:...
\end{comment}

@@

\subsection{Transition Rate Calculation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Time-of-flight and Steady State Velocity Calculation}
The multiscale model defines a graph $\mathbf{G}$ with an adjacency matrix $\mathbf{W}$, where the nodes represent molecules and the edge weights $\omega_{ij}$ represent the Marcus rate from molecule $i$ to molecule $j$. 
The charge dynamics are modeled as a continuous-time random walk on this graph. In the time-of-flight (ToF) model, some vertices serve as \textit{Source} nodes, representing the electrode where charge carriers are injected, and some as \textit{Sink} nodes, where charge carriers are detected and the ToF is recorded.

@@

\begin{equation}
    v_\text{SS} = \sum_i \pi_i \sum_j \omega_{ij} || \vec{r}_{ij}||_2
\end{equation} 
where $\omega_{ij}$ is the charge transition rate from molecule $i$ to molecule $j$, and $\vec{r}_{ij}=\vec{r}_j - \vec{r}_i$ is the center-of-mass (COM) distance vector. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this study, we investigate the hole-transporting organic semiconductor MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene) and study its charge mobility's dependence on HFX.

Atomic charges and molecule polarizability $P_\text{iso}$ are crucial for evaluating molecular energy contributions from electrostatic and polarization effects. A physical property related to the overall atomic charges is dipole moment at charge neutral state. 
To demonstration the effect of HFX on the atomic charges and molecule polarizability $P_\text{iso}$,
Figure \ref{fig:autogen_MADN}(a)(b) illustrates the dependence of the dipole moment $\mu$ and isotropic polarizability $P_\text{iso}$ on HFX.
Figure \ref{fig:autogen_MADN}(c)(d) show 
The reorganization energy $\lambda$ and energy disorder $\sigma(E)$ as a function of HFX parameter are also shown in Fig .\ref{fig:autogen_MADN}(c)(d).

%
\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\textwidth]{figs/fig_autogen.pdf}
    \caption{(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters (denoted by $\alpha$).}
    \label{fig:autogen_MADN}
\end{figure}
%

From Fig. \ref{fig:autogen_MADN}(a) one can notice a mild decrease in the dipole moment with increasing HFX and in Fig. \ref{fig:autogen_MADN}(b) a linear decrease in isotropic polarizability for both neutral and charged MADN states as HFX increases from 0 to 0.25, indicating reduced molecular polarizability.
Figure \ref{fig:autogen_MADN}(c) indicates an increase in reorganization energy $\lambda$ with higher HFX, reflecting greater energy requirements for electronic adjustments during charge transfer. This increase is nonlinear compared to the linear decrease in $P_\text{iso}$.
Figure \ref{fig:autogen_MADN}(d) shows that the energy disorder $\sigma(E)$ for MADN are similar and close to \unit[0.08]{eV} under different HFX values.

To calculate the ToF from the electronic structures, the \textit{Source} region contains molecules with X-coordinate $0 < r^x_i < 0.5$ nm, and the \textit{Sink} region contains molecules with X-coordinate $8.5 < r^x_i < 9$ nm.

The ToF is also calculated without energy disorder, meaning $\Delta E_{ij}=0$ for all $i,j$.
Table \ref{tab:ToF_MADN_HFX} shows the ToF and corresponding diffusive velocity $v_\text{ToF}$.
With energy disorder, the ToF increases by a factor of approximately 15 as $\alpha$ increases from 0 to 0.25.  
While without energy disorder, the increase factor is about 4. This increase in ToF is attributed to the rise in $\lambda$, changes in molecular energies, and variations in coupling elements.

@@

Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using $\alpha$ = 0.25 (PBE0 functional) as a reference. The energies consistently fall within the range of -0.5 to -1.1 eV, with data points clustering near the diagonal line, indicating similar molecular energies regardless of HFX variation.
To quantify the similarity between two empirical distribution, Wasserstein distance is used.
Denote the empirical distribution of molecular energy $E$ at $\alpha=0$ to be $P_{E(\alpha=0)}$. 
The 1-Wasserstein distance between $P_{E(\alpha=0)}$ and $P_{E(\alpha=0.25)}$ is calculated as:
\begin{equation}
    W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)}) = (\frac{1}{N} \sum\limits_{i=1}^N | E_{i,\text{order}}(\alpha=0) - E_{i,\text{order}}(\alpha=0.25) |)
\end{equation}
where $E_{i,\text{order}}(\alpha=0)$ is the order statistics of $E_i(\alpha=0)$. The 1-Wasserstein distance between two empirical distributions for each plot in Fig. \ref{fig:E_qmmm_MADN} is shown in Table \ref{tab:W2_E}. $W_1 (P_{E(\alpha=0)}, P_{E(\alpha=0.25)})$ has range between 0.0045 to 0.0091, indicating that such molecule energy on average has difference less than 2\% since the energy has range from -0.5 to -1.1 eV.

\begin{table}[H]
    \centering
    \begin{tabular}{c c c c c c}
    \hline
 $\alpha'$ & 0 & 0.05 & 0.10 & 0.15 & 0.20 \\
    \hline
 $W_1 (P_{E(\alpha')}, P_{E(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
 $W_1 (P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ &  0.010 & 0.012 & 0.0089 & 0.0070 & 0.0032 \\
 $W_1 (P_{E^\text{polar}(\alpha')}, P_{E^\text{polar}(\alpha=0.25)})$ &  0.0065 & 0.0043 & 0.0027 & 0.0023 & 0.0031 \\
 $W_1 (P_{\log_{10}(J_{ij}^2)(\alpha')}, P_{\log_{10}(J_{ij}^2)(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
    \hline
    \end{tabular}
    \caption{The 1-Wasserstein distance between the distributions pair of molecule energy $P_{E(\alpha)}$, electrostatic energy $P_{E^\text{el}(\alpha)}$, polar energy $P_{E^\text{polar}(\alpha)}$ and $P_{\log_{10}(J_{ij}^2)(\alpha)}$. }
    \label{tab:W2_E}
\end{table}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.99\textwidth]{figs/scatterE_qmmm.pdf}
    \caption{Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
    \label{fig:E_qmmm_MADN}
\end{figure}

Figures \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} show that both electrostatic and polarization energies remain consistent close across HFX values from 0 to 0.25, since all the points comparing $E_i(\alpha')$ and $E_i(\alpha=0.25)$ in the scatter plot are close to the diagonal line.
The 1-Wasserstein distance between the distribution of $E^\text{el}$ calculated by $\alpha'$ and that calculated by $\alpha=0.25$, $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$, is shown at Table \ref{tab:W2_E}. It shows that $W_1(P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ is at maximum 0.012. The 1-Wasserstein distance between the $E^\text{polar}$ distribution calculated by $\alpha'$ and that calculated by $\alpha=0.25$ is also shown in Table .\ref{tab:W2_E}, with a maximum of 0.006. So the small Wasserstein distances suggest that the using different $\alpha'$ other than $\alpha=0.25$, the data of $E, E^\text{el}, E^\text{polar}$ have not changed significantly.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.99\textwidth]{figs/scatterEstat_qmmm.pdf}
    \caption{Scatter plot of MADN electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
    \label{fig:Estat_qmmm_MADN}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.99\textwidth]{figs/scatterEdip_qmmm.pdf}
    \caption{Scatter plot of MADN polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
    \label{fig:Edip_qmmm_MADN}
\end{figure}

@@

The coupling element obtained with different HFX for each molecular pair compared to that obtained with HFX=0.25 is shown in the scatter plot Fig. \ref{fig:J_MADN}.
\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/scatterJ_all.pdf}
    \caption{Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
    \label{fig:J_MADN}
\end{figure}

The distribution of $\log_{10} J^2$ has a range of -14 to -2, and for all HFX values, the distribution has a peak at around -5. 
For large values $\log_{10} J^2 < -5$ the coupling element calculated from $\alpha'=0, 0.05, 0.10, 0.15, 0.2$ remains consistently close to that calculated by $\alpha=0.25$. While for small values $\log_{10} J^2 > -5$, the $\alpha'$ calculated coupling elements for a specific molecular pair can have large variation compared to $\log_{10} J^2$ calculated using $\alpha=0.25$.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{figs/fig_network_all.pdf}
    \caption{The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$. The molecular systems obtained by different HFX are colored according to the legend.}
    \label{fig:J_percolate}
\end{figure}
After performing percolation algorithm, Figure \ref{fig:J_percolate} shows the dependence of $\max({N_\text{sub}})$ on the critical value $J_c$. When $\log_{10} J_c^2 < -4.5$, $\max({N_\text{sub}})$ is 1000, meaning that removing all the edges with $J^2 < 3.1 \times 10^{-5}$ the 1000 vertexes still form a connected graph. 
But when removing the edges with $J^2 < 3.1 \times 10^{-4}$ ( corresponding to $J_c > -3.5$), the maximum size subgraph is 600, and it quickly decreases as $J_c$ increases, showing a phase transition. 
So the dominated coupling elements are those with $\log_{10} J_c^2 > -4.5$. 
And the variation in small $J$ due to HFX has less impact on the charge dynamics.

@@

\subsection{ToF Distribution}
The ToF is calculated from electronic structure ($E$, $\lambda$ and $\log_{10}(J^2)$) data, that is, ToF is a function with the input of all electronic structure parameters:
\begin{equation}
    %\tau = g(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \}) \;
    \tau = g(x_1, x_2, \cdots, x_{N_d})
    \label{eq:tau1}
\end{equation}
The input $(x_1, x_2, \cdots, x_{N_d})$ represents the collection of the parameters $$(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \})$$  where $N_d$ is the parameter dimension, that is the number of input parameters. 
And $\{E_i|i=1,2,\cdots,N \}$ is the ordered set whose elements are the molecule energy,
$\{J_{ij}|i,j=1,2,\cdots,N \}$ is the ordered set whose elements are the coupling elements.

Since the exchange-correlation functional is not known and each molecule has a slightly different structure compared to the optimized structure, each parameter has uncertain. 
To estimate the uncertainty, we consider the maximum amount of uncertainties according to the obtained $(\lambda, \{E_i|i=1,2,\cdots,N \}, \{J_{ij}|i,j=1,2,\cdots,N \})$ with the six different HFX.
To achieve this, each parameter can be modeled as a normal distribution with the mean and standard deviation obtained by the maximum likelihood estimation. For a normal distribution, they are respectively the sample mean and standard deviation obtained by six varying HFXs.

Then Monte Carlo scheme is used to estimate the distribution of the ToF. The Monte Carlo scheme has the procedure:
\begin{enumerate}
\item For all $i,j=1,2,\cdots, N_d$, obtain a realization $(x_1, x_2, \cdots, x_{N_d})$ where each parameter has the normal distribution, meaning the corresponding electronic parameters are sampled from the distribution $\lambda_i \in \mathcal{N}(\mathbb{E}(\lambda), \mathbb{V}(\lambda))$, $E_i \in \mathcal{N}(\mathbb{E}(E_i), \mathbb{V}(E_i))$, $\log_{10}(J_{ij}^2) \in \mathcal{N}(\mathbb{E}(\log_{10}(J_{ij}^2)), \mathbb{V}(\log_{10}(J_{ij}^2)))$. 
\item Calculate ToF using the sampled data set $(x_1, x_2, \cdots, x_{Nd})$. 
\item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain ToFs. Plot the distribution of the ToFs.
\item Estimate the 99\% confidence interval around the median.
\end{enumerate}

%From equation \ref{eq:hitting_time}, the ToF can be considered as the some combination of occupation time in the molecules, which is $log_{10}(\omega_{i}^{-1})$. 
%When the parameters $E, J_{ij}, \lambda_{ij}$ are normally distributed random variables, the calculated ToF shows that variables $E,\lambda_{ij}$ has a larger influence than $J_{ij}$. 
%The Marcus rate uses $E,\lambda_{ij}$ in the exponential form. If $\Delta E$ is normally distributed, then $log_{10}(\omega_{i}^{-1})$ is Gamma distributed. 
%Since $E$ has greater influence to ToF than $\lambda_{ij}, J_{ij}$ and to be consistent, Gamma distribution is used to fit the Monte Carlo sampled ToF in all the investigated cases.

\begin{comment}
    Sampling the molecule energy as a normal distribution $E_i \sim \mathcal{N}(\bar{E}_i, \sigma_{E_i})$ will potentially destroy the energy correlation, especially for correlated systems, resulting a shift in the ToF calculation.
But we will show that making the molecule energy uncorrelated in the MADN system will not cause such a shift in ToF. 
To do so, let $\{E_1, E_2, \cdots, E_N\}^{\alpha}$ be an ordered set with elements being the energy calculated using a specific $\alpha$ value. 
Then the order of the energies are randomly shuffled so that they are no longer correlated, and denote it as $\{E_1, E_2, \cdots, E_N\}^{\alpha}_{\text{shuffle}}$. The ToF calculated using the shuffled energy is $ \tau_{\text{sh}} = \tau(\{E_1, E_2, \cdots, E_N\}^{\alpha}_{\text{shuffle}}) $.
%
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{figs/ToFx_shuffle.pdf}
    \caption{Distribution of $\tau_{\text{sh}}$ calculated using shuffle energies. Each distribution are a sample of 10000 $\tau_{\text{shuffle}}$. The position of the solid circle indicates the ToF calculated from the specific $\alpha$ value, and the position of the solid square indicates the average $\tau_{\text{shuffle}}$ over the 10000 samples.}
    \label{fig:ToF_shuffle_MADN}
\end{figure}
%
After such shuffling energy and ToF calculation for 10000 times, the distribution of $\tau_{\text{sh}}$ are shown in Fig.\ref{fig:ToF_shuffle_MADN}. 
For the chosen $\alpha=0.05, 0.15, 0.25$, the $\tau_{\text{sh}}$ does not overall shift to smaller or large values, and the averaged $\tau_{\text{sh}}$ is close to the ToF obtained without energy shuffle.
So making the energy uncorrelated will not shift the ToF to smaller or larger values.
This enables representing the parameter uncertainties in $\lambda, \{E_i\}, \{ J_{ij}\}$ by the normal distribution without shift the ToF.
\end{comment}

To understand how the uncertainty pass from $E, \lambda, J_{ij}$ to ToF, the parameter control is used. That is, a set of parameter, such as $E_i$ for all $i=1,2,\cdots,N$ is choose while keeping other parameter fixed, then performed Monte Carlo sampling to obtain ToF distribution and estimate upper and lower confidence bound.
Then we use Sobol total indices to analyze and quantify 
which uncertainty among $E, \lambda, J_{ij}$ has a greater impact on the ToF,
